---
title: "Processing microbiome data with dada2"
output: BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Processing microbiome data with dada2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

Before we start, there are better references that the ones I can provide in this document:

* [Original package website](https://benjjneb.github.io/dada2/)

* [Article with a more complex workflow](https://f1000research.com/articles/5-1492/v2)

As always, to load the package, we have to use the command:

```{r setup,eval=TRUE,message=FALSE,warning=FALSE}
library(microbiome.onglab)
```

to load the package. 

# Scripts to run

Generally speaking, there are many script to run. The main focus of this wrapper is on efficiency, so for every scripts in the directory:

```{r pack}

system.file("scripts",package = "microbiome.onglab")
list.files(system.file("scripts", package = "microbiome.onglab"))

```

For every one of these scripts (except `create_file_structure.R`), there are one/two functions that generates an associated [condor](https://research.cs.wisc.edu/htcondor/) file, and whenever is necessary another `json` file with the parameters for that process. 


## Example with the filter and trim step

Even though this is the first step, the remaining steps follow a similar structure. In general, for every step, there are going to be 2 `R` functions, one that generates the `json` parameters, and one that runs the script with condor. For the `filter and trim` step, we would have the run:

```{r param_file,warning=FALSE}
param_file <- tempfile(fileext = ".json")
dada2_param_filter_trim(param_file)
```

This generates a json parameter file, which needs to be edited with parameters that depend on the unique characteristics of the experiment.

```{r param_file_show, echo = FALSE,warning=FALSE,results='hold'}

cat(readLines(param_file))

```

Similarly, the `condor_filter_trim` function, would generate a file that needs to be edited, and then submitted to condor.

```{r , condor,warning=FALSE}
condor_file <- tempfile(fileext = ".cdr")
condor_filter_trim(condor_file = condor_file)

```

The file looks as follows, and in this case at least the `queue_file`, `param_file`, and `outdir` would have to be manually edited.

```{r condor_file_show, echo = FALSE,warning=FALSE}

cat(readLines(condor_file),sep = "\n")

```


# Running all together

We define the temp directory:

```{r run_all, warning=FALSE}

my_dir = file.path(tempdir(),"example")
my_dir

create_file_structure(my_dir)

dir.create(file.path(my_dir,"dada2_params"))
dada2_param_copy_all(outdir =  file.path(my_dir,"dada2_params"), prefix = "example")
dir.create(file.path(my_dir,"condor"))
condor_generate_all(condordir = file.path(my_dir,"condor"),prefix = "example")

```

After doing these steps, the project directory will have the following structure:

```{r}

list.files(my_dir,recursive = TRUE,include.dirs = TRUE)

```

## Running in condor

After filling all the condor text files, these commands will run the whole pipeline

```{bash, eval = FALSE}

condor_submit condor/example_dada2_filter_and_trim_2019_08_20
condor_submit condor/example_dada2_learned_error_rates_2019_08_20
condor_submit condor/example_dada2_merge_pairs_2019_08_20           
condor_submit condor/example_dada2_make_seqtab_2019_08_20    
condor_submit condor/example_dada2_remove_chimeras_2019_08_20
condor_submit condor/example_dada2_label_taxa_2019_08_20        

```

# Quality control after processing



