---
title: "Procesing microbiome data with dada2"
output: BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Procesing microbiome data with dada2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

Before we start, there are better references that the ones I can provide in this document:

* [Original package website](https://benjjneb.github.io/dada2/)

* [Article with a more complex workflow](https://f1000research.com/articles/5-1492/v2)

As always, to load the package, we have to use the command:

```{r setup,eval=TRUE,message=FALSE,warning=FALSE}
library(microbiome.onglab)
```

to load the package. 

# Scripts to run

Generally speaking, there are many script to run. The main focus of this wrapper is on efficiency, so for every scripts in the directory:

```{r pack}

system.file("scripts",package = "microbiome.onglab")
list.files(system.file("scripts", package = "microbiome.onglab"))

```

For every one of these scripts (except `create_file_structure.R`), there are one/two functions that generates an associated [condor](https://research.cs.wisc.edu/htcondor/) file, and whenever is necessary another `json` file with the parameters for that process. 

## Example with the filter and trim step








